Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-06-13 analysis/dendro_summary.Rmd
update

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
library("pander")

@@

@@

>>>>

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
library("pander")
library("here")

```{r}
# Compara 
comparaKW <- function(df, mivariable){ 
  require(PMCMR)
  require(multcompView)

  output <- list()

  # Model formulation
  myformula <- as.formula(paste0(mivariable, " ~ site"))

  # Kruskal Wallis  
  kt <- kruskal.test(myformula, data = df)

  # Summary AOV (broom style)
  tm <- broom::tidy(kt)
  tm$mi_variable <- mivariable

  # Dunn's test 
  object <- posthoc.kruskal.dunn.test(myformula, data=df, p.adjust.method = "bonferroni")

  # Get dataframe with letters and pvalues (#from summary.PMCMR)
  pval <- as.numeric(object$p.value)
  stat <- as.numeric(object$statistic)
  grp1 <- as.numeric(c(col(object$p.value)))
  cnam <- colnames(object$p.value)
  grp2 <- as.numeric(c(row(object$p.value)))
  rnam <- rownames(object$p.value)
  H0 <- paste(cnam[grp1], " = ", rnam[grp2])
  OK <- !is.na(pval)
  xdf <- data.frame(H0 = H0[OK], statistic = stat[OK], p.value = format.pval(pval[OK], 5))

  # Get letters (using multcompView) See viggnete PMCMR 
  dt_letters  <- multcompView::multcompLetters(get.pvalues(object), threshold = 0.05)

  output$KW <- tm
  output$post_hoc <- xdf
  output$letters <- dt_letters
  return(output)
  }

@@

comparaAges <- comparaKW(rwl_stat_sites, 'year')

letrasAges <- data.frame(site = names(comparaAges$letters$Letters),
                            age_l = comparaAges$letters$Letters)

age_sites <- age_sites %>% inner_join(letrasAges, by ='site')

@@

```{r}

cofecha <- read_delim(here::here("/data_raw/dendro_ring/cofechas.csv"), delim = ";") %>% 
  mutate(site = as.factor(site))

rbt <- cofecha %>% 
  group_by(site) %>% 
  summarise(rbt = mean(corr_w_master))

### 2019-06-13 man/tables/t_dendro_summary.Rmd
update

**Table 2.** Characteristics of the mean tree ring chronologies. Values of the length year in parenthesis indicate years replicated more with than five series. RW = mean annual ring width (standard deviation in parenthesis). MS = mean sensitivity. AR(1) = mean autocorrelation of raw series. Rbt = mean correlation between series. EPS = mean expressed population signal. EPS and Rbt are calculated for the mean residual chronologies of growth indices.

```{r}
dendro_summ <- read.csv(here::here("/data/dendro_summary", "site3_dendro_summary.csv"), header = TRUE)

@@

t2 <- t1raw %>% 
  mutate(pare = ")") %>% 
  mutate_at(c(8:13), round, 3) %>% 
  unite(length_year, c(length_year,length_year5), sep=" (") %>%
  mutate_at(.vars = c("rw_mean","rw_std"), funs(formatC(., digits = 3, format = 'f'))) %>% 
  unite(RW, c(rw_mean,rw_std), sep=" (") %>%
  mutate(
    length_year = paste0(length_year, pare),
    RW = paste0(RW, pare)) %>% 
  dplyr::select(name, first_year, last_year, 
  length_year, n_trees, n_radii,
  RW, ms2, ar1, rbar.wt, eps, -pare, -site)

ta2 <- regulartable(t2, col_keys =c("name", "first_year", "last_year", "n_trees", "n_radii", "RW", "ms2",
                                   "ar1","rbar.wt","eps"))
ta2 <- ta2 %>% set_header_labels(name = "Site", first_year = "First year", last_year = "Last year",
                                 length_year = "Length (years)", n_trees ="# trees", n_radii = '# cores',
                                 RW ="RW (mm)", ms2="MS", ar1="AR(1)", rbar.wt = "Rbt", eps = "EPS") %>%
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 10) %>% 
  fontsize(part = "body", size = 9) %>% 
  autofit(add_w = 0, add_h = 0) %>% 
  align(align = "center")

>>>>

**Table 2.** Characteristics of the mean tree ring chronologies. Values of the length year in parenthesis indicate years replicated with more than five series. RW = mean annual ring width (standard deviation in parenthesis). MS = mean sensitivity. AR(1) = mean autocorrelation of raw series. Rbt = mean correlation between series. EPS = mean expressed population signal. EPS and Rbt are calculated for the mean residual chronologies of growth indices.

```{r}
dendro_summ <- read.csv(here::here("/data/dendro_summary", "site3_dendro_summary.csv"), header = TRUE)
cofecha <- read_delim(here::here("/data_raw/dendro_ring/cofechas.csv"), delim = ";")

rbt <- cofecha %>% 
  group_by(name = site) %>% 
  summarise(rbt = mean(corr_w_master))

@@

t2 <- t1raw %>% 
  inner_join(rbt, by="name") %>% 
  mutate(pare = ")") %>% 
  mutate_at(c(8:13), round, 3) %>% 
  unite(length_year, c(length_year,length_year5), sep=" (") %>%
  mutate_at(.vars = c("rw_mean","rw_std"), funs(formatC(., digits = 3, format = 'f'))) %>% 
  unite(RW, c(rw_mean,rw_std), sep=" (") %>%
  mutate(
    length_year = paste0(length_year, pare),
    RW = paste0(RW, pare)) %>% 
  dplyr::select(name, first_year, last_year, 
  length_year, n_trees, n_radii,
  RW, ms2, ar1, rbt, -rbar.wt, eps, -pare, -site)

ta2 <- regulartable(t2, col_keys =c("name", "first_year", "last_year", "length_year", "n_trees", "n_radii", "RW", "ms2",
                                   "ar1","rbt","eps"))
ta2 <- ta2 %>% set_header_labels(name = "Site", first_year = "First year", last_year = "Last year",
                                 length_year = "Length (years)", n_trees ="# trees", n_radii = '# cores',
                                 RW ="RW (mm)", ms2="MS", ar1="AR(1)", rbt = "Rbt", eps = "EPS") %>%
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 10) %>% 
  fontsize(part = "body", size = 9) %>% 
  autofit(add_w = 0, add_h = 0) %>% 
  align(align = "center")

### 2019-06-13 man/tables/t_huber_res_bai.Rmd
update tables
update

---
output:  
  word_document:
    reference_docx: "../../man/template_tables_portrait.docx"
---

@@

**Table S2.** Robust measures of central tendency of resilience indices for tree-growth (BAI) groupped by drought events, site and interaction. Measures of central tendency are M-estimators based on Huber's Psi (see material and methods). 95 % confidence intervals using 3000 bootstrap are included in parentheses.

>>>>

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

**Table S2.** Robust measures of central tendency of resilience indices for tree-growth (BAI) grouped by drought events, site and interaction. Measures of central tendency are M-estimators based on Huber's Psi (see material and methods). 95 % confidence intervals using 3000 bootstrap are included in parentheses.

### 2019-06-13 man/tables/t_sampled_plots.Rmd
update

t1 <- t1raw %>% dplyr::select(
  name, lat_m, long_m, elev_min, elev_max, slope_mean, slope_sd, prec, temp, 
  n_trees, n_radii, dn_mean, dn_sd, h_mean, h_sd, age_mean, age_std, 
  dn_mean_all, dn_sd_all, h_mean_all, h_sd_all,
  ba_mean, ba_sd, stand_density_mean, stand_density_sd, srd_mean, srd_sd,
  all_dn_l, all_h_l, ba_l, ft_dn_l, ft_h_l, std_l, srd_l
  ) %>% 
  mutate(pare = ")") %>% 
  mutate_at(c("lat_m","long_m","slope_mean","slope_sd","ba_mean","ba_sd","srd_mean","srd_sd"), 
            funs(formatC(., digits = 2,format='f'))) %>%  
  mutate_at(.vars = c("prec"), funs(format(., digits = 0))) %>% 
  # mutate_at(c(10:19, 22:23), round, 1) %>% 
  mutate_at(c("dn_mean","dn_sd","h_mean","h_sd","age_mean","age_std","dn_mean_all","dn_sd_all","h_mean_all","h_sd_all","stand_density_mean","stand_density_sd"),
            funs(formatC(., digits = 1,format='f'))) %>%
  mutate_at(c("elev_min", "elev_max"), funs(round(., 0))) %>% 
  unite(elev, c(elev_min, elev_max), sep= " - ") %>% 
  unite(slope, c(slope_mean, slope_sd), sep=" (") %>% 
  unite(n_trees, c(n_trees, n_radii), sep=" (") %>% 
  unite(dn, c(dn_mean, dn_sd), sep=" (") %>% 
  unite(h, c(h_mean, h_sd), sep=" (") %>% 
  unite(age, c(age_mean, age_std), sep=" (") %>% 
  unite(dn_all, c(dn_mean_all, dn_sd_all), sep=" (") %>% 
  unite(h_all, c(h_mean_all, h_sd_all), sep=" (") %>% 
  unite(ba, c(ba_mean, ba_sd), sep=" (") %>% 
  unite(stand_density, c(stand_density_mean, stand_density_sd), sep=" (") %>% 
  unite(srd, c(srd_mean, srd_sd), sep=" (") %>% 
  mutate(
    slope = paste0(slope, pare),
    n_trees = paste0(n_trees, pare),
    dn = paste(paste0(dn, pare), ft_dn_l, sep=" "),
    h = paste(paste0(h, pare), ft_h_l, sep = ' '),
    age = paste0(age, pare),
    dn_all = paste(paste0(dn_all, pare), all_dn_l, sep = ' '),
    h_all = paste(paste0(h_all, pare), all_h_l, sep = ' '),
    ba = paste(paste0(ba, pare), ba_l, sep = ' '),
    stand_density = paste(paste0(stand_density, pare), std_l, sep = ' '),
    srd = paste(paste0(srd, pare), srd_l, sep = ' ')) %>%
  dplyr::select(-pare, -all_dn_l, -all_h_l, -ba_l, -ft_dn_l, -ft_h_l, -std_l, -srd_l)

@@

>>>>

t1 <- t1raw %>% dplyr::select(
  name, lat_m, long_m, elev_min, elev_max, slope_mean, slope_sd, prec, temp, 
  n_trees, n_radii, dn_mean, dn_sd, h_mean, h_sd, age_mean, age_std, age_l, 
  dn_mean_all, dn_sd_all, h_mean_all, h_sd_all,
  ba_mean, ba_sd, stand_density_mean, stand_density_sd, srd_mean, srd_sd,
  all_dn_l, all_h_l, ba_l, ft_dn_l, ft_h_l, std_l, srd_l
  ) %>% 
  mutate(pare = ")") %>% 
  mutate_at(c("lat_m","long_m","slope_mean","slope_sd","ba_mean","ba_sd","srd_mean","srd_sd"), 
            funs(formatC(., digits = 2,format='f'))) %>%  
  mutate_at(.vars = c("prec"), funs(format(., digits = 0))) %>% 
  # mutate_at(c(10:19, 22:23), round, 1) %>% 
  mutate_at(c("dn_mean","dn_sd","h_mean","h_sd","age_mean","age_std","dn_mean_all","dn_sd_all","h_mean_all","h_sd_all","stand_density_mean","stand_density_sd"),
            funs(formatC(., digits = 1,format='f'))) %>%
  mutate_at(c("elev_min", "elev_max"), funs(round(., 0))) %>% 
  unite(elev, c(elev_min, elev_max), sep= " - ") %>% 
  unite(slope, c(slope_mean, slope_sd), sep=" (") %>% 
  unite(n_trees, c(n_trees, n_radii), sep=" (") %>% 
  unite(dn, c(dn_mean, dn_sd), sep=" (") %>% 
  unite(h, c(h_mean, h_sd), sep=" (") %>% 
  unite(age, c(age_mean, age_std), sep=" (") %>% 
  unite(dn_all, c(dn_mean_all, dn_sd_all), sep=" (") %>% 
  unite(h_all, c(h_mean_all, h_sd_all), sep=" (") %>% 
  unite(ba, c(ba_mean, ba_sd), sep=" (") %>% 
  unite(stand_density, c(stand_density_mean, stand_density_sd), sep=" (") %>% 
  unite(srd, c(srd_mean, srd_sd), sep=" (") %>% 
  mutate(
    slope = paste0(slope, pare),
    n_trees = paste0(n_trees, pare),
    dn = paste(paste0(dn, pare), ft_dn_l, sep=" "),
    h = paste(paste0(h, pare), ft_h_l, sep = ' '),
    age = paste(paste0(age, pare), age_l, sep = ' '),
    dn_all = paste(paste0(dn_all, pare), all_dn_l, sep = ' '),
    h_all = paste(paste0(h_all, pare), all_h_l, sep = ' '),
    ba = paste(paste0(ba, pare), ba_l, sep = ' '),
    stand_density = paste(paste0(stand_density, pare), std_l, sep = ' '),
    srd = paste(paste0(srd, pare), srd_l, sep = ' ')) %>%
  dplyr::select(-pare, -all_dn_l, -all_h_l, -ba_l, -ft_dn_l, -ft_h_l, -std_l, -srd_l, -age_l)

@@

ta <- compose(
  ta, j = "ba", part = "header",
  value = as_paragraph(
     "BA\n(m",  
     as_chunk("2", props = fp_text(vertical.align = "superscript", font.size = 8)),
     " ha", 
     as_chunk("-1", props = fp_text(vertical.align = "superscript", font.size = 8)),
     ")"

  )
)

ta <- compose(
  ta, j = "stand_density", part = "header",
  value = as_paragraph(
     "Density\n(trees ha",  
     as_chunk("-1", props = fp_text(vertical.align = "superscript", font.size = 6)),
     ")"

  )
)
